MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-20 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{Community Utility}

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed.

\begin{equation}\label{out_c}
U_{C} = (Et_{C} - Exp1_{C} - Exp2_{C}) \times Th_{C} \times A_{C}
\end{equation}

>>>>

\subsection{Community Revenue}

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed. The utility of a collaborative group of services $U_{C}$ is the revenue of the community. Formula \ref{u_c_normal} is an estimation of the gain of the community.

\begin{equation}\label{u_c_normal}
U_{C} = \big((\alpha \times (A_{C} + Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
\end{equation}

The estimation can be improved specially on cases where the input task rate is high and services are under high load of tasks. The \emph{weighted fair queuing} method of task distribution would distribute tasks based on individual throughput $(Th_{w})$ value of services within community, the services with higher throughput within the community will affect the overall utility of community more since they would proportionally do more of the tasks.

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&{\bigg(\big((\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)}
\end{split}
\end{equation}
